### 2021-03-02 treatise-context/1_introduction.tex
Slight rev contribution

To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x:A:x::x:} {
\NC \V {x} _{\SB {\MS {A}}}
=\NC \V {x} \NR
}
%
with
%
\DispNum {A:A:s::s:} {
\NC \Nm {\MS {A}} \leq \NC s. \NR
}

@@

Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].

@@

Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.

@@

Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.

In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
In chapter 3, we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.

>>>>

To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
We use subscript in square brackets, like \m {\MS {A}}, to denote extraction of components.
That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x:A:x::x:} {
\NC \V {x} _{\SB {\MS {A}}}
=\NC \V {x} \NR
}
%
with
%
\DispNum {A:A:s::s:} {
\NC \Nm {\MS {A}} \leq \NC s. \NR
}

@@

Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability and is nearly optimal \cite [CaT07].
The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].

@@

Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
However, there seems to be no work by now which addresses the constraint of hybrid beamforming.

@@

Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
Indeed, if DS is shown to be optimal \cite [CaT07], then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary in less ideal situations.

In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
Because of the hybrid structure, here it is not possible to generate the sensing matrix by i.i.d.\ entries, which requires a fully digital structure.
But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.

### 2021-03-02 treatise-context/5_conclusion.tex
minor typos
Slight rev contribution

The treatise aims to answer the problem of effective estimation of the MIMO millimeter wave channel by exploiting its sparsity.
To do so, we try the Dantzig Selector (DS) for channel estimation.
We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamformer for the hybrid structure.
We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
Regarding the complexity, we also suggested several ways to reduce it without losing much performance, as justified by simulation.
Simulation is done, and we see that DS indeed outperforms other methods.

We believe that DS is more accurate while having higher complexity.
When the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
Therefore, DS may be used in the scenario that precision is crucial, and in the scenario that the number of RF chain is more limited or fewer stages of estimation is possible.

>>>>

The treatise aims to answer the problem of effective estimation of the MIMO millimeter wave channel by exploiting its sparsity.
To do so, we try the Dantzig Selector (DS) for channel estimation.
We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamforming matrix for the hybrid structure.
We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
Regarding the complexity, we also suggested several ways to reduce it without losing much performance, as justified by simulation.
Simulation is done, and we see that DS indeed outperforms other methods.

We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
Since DS is more accurate while having higher complexity, when the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
Therefore, DS may be used in the scenario that precision is crucial, as well as that the number of RF chain is more limited or fewer stages of estimation is possible.

### 2021-03-02 treatise-pdflatex/1_introduction.tex
Slight rev contribution

To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
That is, if there is some \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x:A:x::x:} {
\V {x} _{\SB {\mathcal {A}}}
=\V {x} 
}
%
with
%
\DispNum {A:A:s::s:} {
\Nm {\mathcal {A}} \leq s. 
}

@@

For concreteness, say \m {\V {z}} is an i.i.d.\ random normal vector.
If so, a stronger result was established \cite {CaT07} that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible.

@@

Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite {CaR05}.

@@

Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.

In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
In chapter 3, we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.

>>>>

To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
We use subscript in square brackets, like \m {\mathcal {A}}, to denote extraction of components.
That is, if there is some \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x:A:x::x:} {
\V {x} _{\SB {\mathcal {A}}}
=\V {x} 
}
%
with
%
\DispNum {A:A:s::s:} {
\Nm {\mathcal {A}} \leq s. 
}

@@

For concreteness, say \m {\V {z}} is an i.i.d.\ random normal vector.
If so, a stronger result was established that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible.

@@

Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability and is nearly optimal \cite {CaT07}.
The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite {CaR05}.

@@

Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
Indeed, if DS is shown to be optimal \cite {CaT07}, then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary in less ideal situations.

In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
Because of the hybrid structure, here it is not possible to generate the sensing matrix by i.i.d.\ entries, which requires a fully digital structure.
But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.

### 2021-03-02 treatise-pdflatex/notation.tex
Slight rev contribution

\starttitle [title={Notation}]

\starttable[|l|l|l|] \HL
Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
\m {\mathfrak {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
\m {\mathfrak {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
\m {\V {a}} \VL vector \VL \AR \HL
\m {\M {A}} \VL matrix \VL \AR \HL
\m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
\m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
\m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
\m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
\m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
\m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
\m {\mathbb {K}} \VL either \m {\mathbb {R}} or \m {\mathbb {C}} \VL  \AR \HL
\m {\mathbb {K} ^{N}} \VL Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}} \VL  \AR \HL
\m {\mathbb {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\m {m\; \mathrm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n} \AR \HL
\m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
 \VL component of \m {\V {a}} \VL  \AR \HL
\m {\mathbb {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
\m {\mathbb {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
\m {\mathsf {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
\stoptable

>>>>

\chapter*{Notation}

\begin{center}
\begin{tabular}{ l | c | r }
\hline
 Expression  &  Meaning or Definition  &  More Explanation  \\ \hline
 \m {\Nm {a}}  &  magnitude  &  for real or complex numbers  \\ \hline
 \m {\mathfrak {Re} \SB {a}}  &  real part  &  for complex numbers  \\ \hline
 \m {\mathfrak {Im} \SB {a}}  &  imaginary part  &  for complex numbers  \\ \hline
 \m {\V {a}}  &  vector  &   \\ \hline
 \m {\M {A}}  &  matrix  &   \\ \hline
 \m {\V {1}}  &  all-1 vector  &  dimension will be specified  \\ \hline
 \m {\V {0}}  &  all-0 vector  &  dimension will be specified  \\ \hline
 \m {\V {a} _{\SB {n}}}  &  \m {n}-th component of \m {\V {a}}  &   \\ \hline
 \m {\M {A} _{\SB {m,n}}}  &  \m {m,n}-th entry of \m {\M {A}}  &   \\ \hline
 \m {\V {a} _{\SB {0}}}  &  the first component of \m {\V {a}}  &    \\ \hline
 \m {\M {A} _{\SB {0,0}}}  &  the upper-left entry of \m {\V {A}}  &    \\ \hline
 \m {\mathbb {K}}  &  either \m {\mathbb {R}} or \m {\mathbb {C}}  &    \\ \hline
 \m {\mathbb {K} ^{N}}  &  Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}}  &    \\ \hline
 \m {\mathbb {K} ^{M \D N}}  &  collection of \m {M} by \m {N} matrices  &    \\ \hline
 \m {m\; \mathrm {Mod}\; n}  &  remainder of \m {m} divided by \m {n}  &  with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n}  \\ \hline
 \m {\VNm {\V {a}} _p}  &  \m {\ell_p}-norm of \m {\V {a}}  &  \m {p >0}  \\ \hline
 \m {\VNm {\V {a}} _\infty}  &  the maximum-magnitude  &   \\ \hline
   &  component of \m {\V {a}}  &    \\ \hline
 \m {\mathbb {P} \SB {A}}  &  probability of event \m {A}  &    \\ \hline
 \m {\mathbb {E} \SB {X}}  &  expectation of random variable \m {X}  &    \\ \hline
 \m {\mathrm {Var} \SB {X}}  &  variance of random variable \m {X}  &    \\ \hline
\end{tabular}
\end{center}
